Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd
citation

Data was analyzed through the R programming software [@citeR] and packages such as `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `knitr` [@knitr], and `dplyr` [@dplyr] were used to help download, clean, simulate, analyze, and test the data. For model construction and analysis, the following packages were used: `rstanarm` [@rstanarm1, @rstanarm2], `brms` [@brms1, @brms2, @brms3], and `bayesplot` [@bayesplot1, @bayesplot2].

>>>>

Data was analyzed through the R programming software [@citeR] and packages such as `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `knitr` [@knitr], and `dplyr` [@dplyr] were used to help download, clean, simulate, analyze, and test the data. For model construction and analysis, the following packages were used: `rstanarm` [@rstanarm1; @rstanarm2], `brms` [@brms1; @brms2; @brms3], and `bayesplot` [@bayesplot1; @bayesplot2].
